Estimating duration in the presence of misclassification

### 2024-03-18 conclusion.tex
Statistical => phenomonological

In \cref{E-transmission}, I found that this it is possible, developing two models that can infer incidence and transmission from prevalence surveys.
One model was statistical in nature and the other mechanistic.
The statistical approach, based on the backcalculation framework, provide estimates of incidence and makes fewer assumptions about the infection process; however, the estimates are very uncertain.
The mechanistic approach, based on a SIR-type compartmental model, reduces the uncertainty and allows estimation of the components of transmission by making stronger assumptions about the infection process.
These results highlighted the heterogeneity across regions and age groups in England.

>>>>

In \cref{E-transmission}, I found that this it is possible, developing two models that can infer incidence and transmission from prevalence surveys.
One model was phenomenological in nature and the other mechanistic.
The phenomenological approach, based on the backcalculation framework, provide estimates of incidence and makes fewer assumptions about the infection process; however, the estimates are very uncertain.
The mechanistic approach, based on a SIR-type compartmental model, reduces the uncertainty and allows estimation of the components of transmission by making stronger assumptions about the infection process.
These results highlighted the heterogeneity across regions and age groups in England.

### 2024-03-18 introduction.tex
Statistical => phenomonological

The models with the weakest assumptions are statistical models.
These make almost no assumptions about the transmission process, viewing incidence as a generic counting process (introduced in full in \cref{E-inc-prev:sec:infection-process}).
The most common model is that incidence follows a Poisson process, and the intensity of the process is the target of inference.
% The use of Poisson processes to model incidence of an infectious disease was very popular in the context of HIV/AIDS\todo{maybe a ref for Poisson in HIV/AIDS?}.

@@

Having estimated the duration of positivity, I then turn to estimating incidence and transmission from the CIS data in \cref{E-transmission}, thus fulfilling the primary aim of this thesis.
I use both a statistical and mechanistic transmission model, contrasting their results and discussing the advantages and disadvantages of each in this context.
Finally, I conclude in \cref{E-conclusion}.

>>>>

The models with the weakest assumptions are \emph{phenomenological} models.
These make almost no assumptions about the transmission process, viewing incidence as a generic counting process (introduced in full in \cref{E-inc-prev:sec:infection-process}).
The most common model is that incidence follows a Poisson process, and the intensity of the process is the target of inference.
% The use of Poisson processes to model incidence of an infectious disease was very popular in the context of HIV/AIDS\todo{maybe a ref for Poisson in HIV/AIDS?}.

@@

Having estimated the duration of positivity, I then turn to estimating incidence and transmission from the CIS data in \cref{E-transmission}, thus fulfilling the primary aim of this thesis.
I use both a phenomenological and mechanistic transmission model, contrasting their results and discussing the advantages and disadvantages of each in this context.
Finally, I conclude in \cref{E-conclusion}.
